Wind veer and speed in turbulent Ekman flow part I: scaling analysis and universal profile model

### 2024-11-20 cover_letter/20241114_coverletter.tex
updated cover letter; consistent lower-case headings in part1

%
This work tackles the problem of a consistent scaling framework across the different layers of the boundary layer,
including the viscous sub-layer, buffer layer, logarithmic layer, Ekman layer, and outer layer.
%
\par
%
In Part I, we approach the problem through DNS at unseen scale separation and domain size, we obtain high-quality data across all
these regimes that allow use to identify some robust features and scaling properties and yield valuable insight
on the scaling of stress, turbulent viscosity and the velocity profiles.
%
As we put a particular focus on the wind veer, the span-wise velocity component (which also accomplishes the Ekman transport)
is of central importance and we identify a novel mixed scaling of the component in the surface layer which allows us
to project the turning of the wind also within the lower part of the surface layer for arbitrary Reynolds number.
% 
\par
%
Part II builds upon these results using large-eddy simulation (LES). We being with an a posteriori validation of the LES where
the DNS set-up is matched as exactly as possible in terms of Reynolds number and the z-nough parameter.
This yields valuable insight regarding the physical convergence of the LES to the DNS solution that serves as a reference here. 
%
Studies in typical, idealized amtmospheric-boundary-layer settings illustrate that the LES results are consistent with
the profile model that has been developed and part I and was calibrated using DNS data, provided the LES uses about 150 grid points to resolve the boundary layer.
%
The LES and the profile model developed are independent paradigms to study the velocity profile. Hence, the perfect agreement of LES and DNS data at low Reynolds number together with the agreement between LES and the profile model evaluated for geophysical Reynolds number suggests that both the LES and the profile model behave in a physical way for high Reynolds number. 
%
\par
%
We believe that our research makes a relevant contribution to the field.
%
The findings of this study, particularly of the surface layer similarity, are consistent and
complementary with atmospheric measurements.
%
The model developed in Part I is of practical relevance for applications in wind-power projection, numerical modelling
and can be used for a-priori testing of turbulence parameterizations in idealized settings. 
%
\par
%
We hope that the manuscript raises your interest and complies with the high standard of Boun\-da\-ry-Layer Meteorology and  would be delighted if the manuscript were considered for publication in the journal.

\grussformelsigniert{With Kind Regards \vspace{-0.25em}}

>>>>

%
This work tackles the problem of a consistent scaling framework across the different layers of the boundary layer,
including the viscous sub-layer, buffer layer, logarithmic layer, Ekman layer, and outer layer. Both papers 
are concerned with the study of idealized, stationary and truly neutral Ekman flow over a smooth surface. 
%
\par
%
In Part I, we approach the problem through DNS at unseen scale separation and domain size, we obtain high-quality data across all
these regimes that allow use to identify some robust features and scaling properties and yield valuable insight
on the scaling of stress, turbulent viscosity and the velocity profiles.
%
As we put a particular focus on the wind veer, the span-wise velocity component (which also accomplishes the Ekman transport)
is of central importance and we identify a novel mixed scaling of the component in the surface layer which allows us
to project the turning of the wind also within the lower part of the surface layer for arbitrary Reynolds number.
% 
\par
%
Part II builds upon these results using large-eddy simulation (LES). We beging with an a posteriori validation of the LES where
the DNS set-up is matched as exactly as possible in terms of Reynolds number and the z-nought parameter.
This yields valuable insight regarding the physical convergence of the LES to the DNS solution that serves as a reference here. 
%
Studies in typical, idealized amtmospheric-boundary-layer settings illustrate that the LES results are consistent with
the profile model that has been developed in part I and was calibrated using DNS data, provided the LES uses about 150 grid points to resolve the boundary layer.
%
The LES and the profile model developed are independent paradigms to study the velocity profile. Hence, the excellent agreement of LES and DNS data at low Reynolds number together with the agreement between LES and the profile model evaluated for geophysical Reynolds number suggests that both the LES and the profile model behave in a physical way for high Reynolds number. 
%
\par
%
We believe that our research makes a relevant contribution to the field.
%
The findings of this study, particularly of the surface layer similarity, are consistent and
complementary with atmospheric measurements.
%
The model developed in Part I is of practical relevance for applications in wind-power projection, numerical modelling
and can be used for a-priori testing of turbulence parameterizations in idealized settings. 
%
\par
%
We hope that the manuscript raises your interest and complies with the high standard of Boun\-da\-ry-Layer Meteorology and  would be delighted if the manuscript were considered for publication in the journal.

With Kind Regards, \vspace{-1em}

\includegraphics[height=1.3cm]{signature_hauke.jpg}~~\includegraphics[height=1.5cm]{signature_transparent.png}\vspace{-2em}

Hauke Wurps \ \ \ \ \ \ \ \ \  Cedrick Ansorge

%\grussformelsigniert{With Kind Regards \vspace{-0.25em}}

### 2024-11-20 write1/manuscript.tex
updated cover letter; consistent lower-case headings in part1

\date{\scriptsize Submitted \today}
\title{Wind Veer and Speed in Turbulent Ekman Flow Part I: Scaling analysis and universal profile model}
\titlerunning{A Universal Velocity Profile for Ekman Flow}
\author{Cedrick Ansorge$^1$ and Hauke Wurps$^{2,3}$}
\authorrunning{C Ansorge and H Wurps}
\institute{$^{1}$\,FU Berlin, Institut f\"ur Meteorologie, Carl-Heinrich-Becker-Weg 6--10, 12165 Berlin, Germany {cedrick@posteo.de}\\
  $^{2}$\,Carl von Ossietzky Universit\"at Oldenburg, School of Mathematics and Science, Institute of Physics \\ 
  $^{3}$\,ForWind - Center for Wind Energy Research, K\"upkersweg 70, 26129 Oldenburg, Germany 
  }

\begin{document} 
%
\maketitle
%
\begin{abstract}
  The profiles of wind speed and direction in turbulent Ekman flow
  are formulated based on asymptotic theory and data from direct numerical simulation. 
  %
  The profile of the streamwise component follows the classical viscous, logarithmic and wake scaling.
  %
  In the outer layer, the velocity component profiles can be described by an Ekman-spiral with adapted
  boundary conditions that result in a reduction of the spiral-like rotation. 
  %
  The span-wise component poses a conceptual challenge to the channel-flow analogy
  in the context of asymptotic matching; it exhibits a mixed scaling in the surface layer, but follows
  outer scaling for most of the outer layer.
  %
  Viscous stress scales universally across the boundary layer in inner units while the total stress
  becomes universal as a function of outer height.
  %
  This implies a mixed scaling for the turbulent stress and eddy viscosity across the inner layer
  and convergence to a universal scaling as function of the outer height across the outer layer
  for increasing scale separation vide Reynolds numbers. 
\end{abstract}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{Introduction}

@@

\noindent\textbf{Author Contributions} CA conceived the study, acquired funding, performed the simulation, analysed and plotted the data for this work. CA and HW interpreted the data and compiled the manuscript. 
\vspace{1em}

@@

\noindent\textbf{Data Availability} The data is available in long-term repositories and indexed by DOIs as cited in the list of references. Further analysis tools and processed data can be made available upon direct request. \vspace{1em}

\noindent\textbf{Conflict of Interest} The Authors declare no competing interest.
\vspace{1em}

\noindent\textbf{Open Access} This article is licensed under a Creative Commons Attribution 4.0 International License, which permits use, sharing, adaptation, distribution and reproduction in any medium or format, as long as you give appropriate credit to the original author(s) and the source, provide a link to the Creative Commons licence, and indicate if changes were made.  To view a copy of this licence, visit \href{http://creativecommons.org/licenses/by/4.0/}{https://creativecommons.org/licenses/by/4.0/}.

>>>>

\date{\scriptsize Submitted \today}
\title{Wind veer and speed in turbulent Ekman flow part I: scaling analysis and universal profile model}
\titlerunning{A Universal Velocity Profile for Ekman Flow}
\author{Cedrick Ansorge$^1$ and Hauke Wurps$^{2,3}$}
\authorrunning{C Ansorge and H Wurps}
\institute{$^{1}$\,FU Berlin, Institut f\"ur Meteorologie, Carl-Heinrich-Becker-Weg 6--10, 12165 Berlin, Germany {cedrick@posteo.de}\\
  $^{2}$\,Carl von Ossietzky Universit\"at Oldenburg, School of Mathematics and Science, Institute of Physics \\ 
  $^{3}$\,ForWind - Center for Wind Energy Research, K\"upkersweg 70, 26129 Oldenburg, Germany 
  }

\begin{document} 
%
\maketitle
%
\begin{abstract}
  The profiles of wind speed and direction in turbulent Ekman flow
  are formulated based on asymptotic theory and data from direct numerical simulation. 
  %
  The profile of the streamwise component follows the classical viscous, logarithmic and wake scaling.
  %
  In the outer layer, the velocity component profiles can be described by an Ekman-spiral with adapted
  boundary conditions that result in a reduction of the spiral-like rotation. 
  %
  The span-wise component poses a conceptual challenge to the channel-flow analogy
  in the context of asymptotic matching; it exhibits a mixed scaling in the surface layer, but follows
  outer scaling for most of the outer layer.
  %
  Viscous stress scales universally across the boundary layer in inner units while the total stress
  becomes universal as a function of outer height.
  %
  This implies a mixed scaling for the turbulent stress and eddy viscosity across the inner layer
  and convergence to a universal scaling as function of the outer height across the outer layer
  for increasing scale separation vide Reynolds numbers. 
\end{abstract}
~\\[1em] 
\textbf{Keywords} Direct Numerical Simulation $\cdot$ Scale Separation $\cdot$ Ekman Layer $\cdot$ Surface Layer $\cdot$ Hodograph

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{Introduction}

@@

\noindent\textbf{Author contributions} CA conceived the study, acquired funding, performed the simulation, analysed and plotted the data for this work. CA and HW interpreted the data and compiled the manuscript. 
\vspace{1em}

@@

\noindent\textbf{Data availability} The data is available in long-term repositories and indexed by DOIs as cited in the list of references. Further analysis tools and processed data can be made available upon direct request. \vspace{1em}

\noindent\textbf{Conflict of interest} The Authors declare no competing interest.
\vspace{1em}

\noindent\textbf{Open access} This article is licensed under a Creative Commons Attribution 4.0 International License, which permits use, sharing, adaptation, distribution and reproduction in any medium or format, as long as you give appropriate credit to the original author(s) and the source, provide a link to the Creative Commons licence, and indicate if changes were made.  To view a copy of this licence, visit \href{http://creativecommons.org/licenses/by/4.0/}{https://creativecommons.org/licenses/by/4.0/}.
